---
title: "A simple Quarto Website... with cats!"
---

This is a Quarto website.

To learn more about Quarto websites visit <https://quarto.org/docs/websites>.


# Let's load our R libraries

As with any other R script, it is good practice to start by loading the libraries you are going to need for your analysis.


```{r}
library(httr2)
library(tidyverse)
```

Mmm this is a lot of information we would like to hide...

## Take two

Adding an execution option: `#| warning: false`


```{r}
#| warning: false

library(httr2)
library(tidyverse)

```

Yeah!!!


# Now we ca start coding!

Did somebody says cat?? Sorry **cute** cat!!

```{r}
req <- request("https://api.thecatapi.com/v1")
resp <- req %>%
  # Then we add on the images path
  req_url_path_append("images/search") %>%
  # Add query parameters _width and _quantity
  req_url_query(`limit` = 1) %>%
  req_perform() %>%
  resp_body_json()

knitr::download_image(resp[[1]]$url)
```

## We might want to hide the code

Of course there is an option for that: `#| echo: false`

```{r}
#| echo: false


req <- request("https://api.thecatapi.com/v1")
resp <- req %>%
  # Then we add on the images path
  req_url_path_append("images/search") %>%
  # Add query parameters _width and _quantity
  req_url_query(`limit` = 1) %>%
  req_perform() %>%
  resp_body_json()

knitr::download_image(resp[[1]]$url)
```