---
title: "Quarto for Data Science Slides (and beyond)"
subtitle: "UC Love Data Week 2025"
format: 
  revealjs:
    slide-number: true
    footer: "Return to the [demonstration website](../index.qmd)"
    theme: slide-styles.scss
---

## Similar feel, different format {#revealjs-format}

- just another Quarto doc
- ...but with `format: revealjs` in the YAML

. . . 

```yaml
---
title: "Quarto for Data Science Slides (and beyond)"
subtitle: "UC Love Data Week 2025"
format: revealjs
---
```

::: {.notes}
Quarto supports a variety of presentation formats, but revealjs is by far the most capable and customizable, while still being incredibly user-friendly. Revealjs is an open source HTML presentation format.
:::

<!-- NEW SLIDE (this is a comment, which won't render on the slide)  -->


## Create a new slide with `##` {#slide-breaks}

```md
## My first slide title

Here's some slide content

## My second slide title {#updated-slug data-menu-title="Updated nav menu title"}
 
Slide two content here!
```

. . . 

<br>

Slide titles become your **URL slug** (unique portion of URL) and **navigation menu title** (see hamburger, bottom left!) [-- but you can modify these!]{.fragment .fade-in}

::: {.notes}
First step is to create
:::


<!-- NEW SLIDE  -->


## Create incremental lists

::: {.incremental}
- make list items
- appear one by one
- by surrounding your list with a div (`:::`content`:::`)
- and applying the `.incremental` class
:::

. . . 

```md
::: {.incremental}
- make list items
- appear one by one
- by surrounding your list with a div (`:::`content`:::`)
- and applying the `.incremental` class
:::

```


<!-- NEW SLIDE  -->


## Incrementally reveal anything

By placing `. . .` between any content

<br>

. . . 

This content appears after a click! 

. . . 

```md
## Incrementally reveal anything

By placing `. . .` between any content

<br>

. . . 

This content appears after a click!

. . .
```

<!-- NEW SLIDE  -->

## Embed code + output 

```{r}
#| eval: true
#| echo: true
#| output-location: column
#| code-line-numbers: "|1-2|7,9|13"
library(httr2)
library(knitr)

req <- request("https://api.thecatapi.com/v1")
resp <- req %>%
  # Then we add on the images path
  req_url_path_append("images/search") %>%
  # Add query parameters _width and _quantity
  req_url_query(`limit` = 1) %>%
  req_perform() %>%
  resp_body_json()

knitr::download_image(resp[[1]]$url)
```

. . .

Code chunk options above:

```md
#| eval: true
#| echo: true
#| output-location: column
#| code-line-numbers: "|1-2|7,9|13"
```


<!-- NEW SLIDE  -->


## Or just the output {#embed-output-only}

```{r}
#| eval: true
#| echo: false
#| output-location: slide
#| fig-align: "center"
#| out-width: "50%"
library(httr2)
library(knitr)

req <- request("https://api.thecatapi.com/v1")
resp <- req %>%
  # Then we add on the images path
  req_url_path_append("images/search") %>%
  # Add query parameters _width and _quantity
  req_url_query(`limit` = 1) %>%
  req_perform() %>%
  resp_body_json()

knitr::download_image(resp[[1]]$url)
```

. . . 

```md
::: {.notes}
Also, you can include speaker notes! Press "S" to activate.
:::
```

::: {.notes}
Also, you can include speaker notes! Press "S" to activate.
:::


## Apply styles using Sass & CSS {#apply-styles}

Update the appearance of your slides by linking a stylesheet in your YAML: 

```yaml
---
title: "Quarto for Data Science Slides (and beyond)"
subtitle: "UC Love Data Week 2025"
format: 
  revealjs:
    theme: my-styles.scss
---
```

. . . 

Import Google Fonts, define [Sass variables](https://quarto.org/docs/presentations/revealjs/themes.html#sass-variables){target="_blank"}, write CSS.


<!-- NEW SLIDE  -->


<!-- --- -->

<!-- ## {#learn-more data-menu-title="Check out the Quarto documentation" background-iframe="https://quarto.org/docs/presentations/revealjs/" background-interactive=true} -->


<!-- NEW SLIDE  -->


---

## Thanks for watching & happy slide-making! {.center}


